---
title: "New data frames"
author: "Julia Oster"
date: "26 5 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# prism
1) prism.cleaned -> rows deleted with >= 50% NAs
```{r}
NAs.per.row = apply(prism,1,function(x){sum(is.na(x))})
prism.cleaned = prism[-which(NAs.per.row >=0.5*ncol(prism)),]
```


# prism.cl
1) lung.cls -> DepMap_ID of all Lung cancer cell lines
```{r}
lung.cls = prism.cl$DepMap_ID[prism.cl$disease=="Lung Cancer"]
```


# prism.exp
1) Zprism.exp -> Z-transformation
```{r}
Zprism.exp = scale(prism.exp)
```
2) LC.prism.exp -> prism.exp data frame only with Lung cancer cell lines
```{r}
# without Z-transformation
lung.cls = prism.cl$DepMap_ID[prism.cl$disease=="Lung Cancer"]
LC.prism.exp = prism.exp[lung.cls,]
```
3) LC.Zprism.exp -> Zprism.exp data frame only with Lung cancer cell lines


# prism.achilles
1) pa_new -> no NAs, 3 rows deleted
```{r}
rmv.rows=apply(prism.achilles,1,function(x){sum(is.na(x))})
pa_new=prism.achilles[-which(rmv.rows>0),]
```
2)LC.prism.achilles -> prism.achilles data frame only with Lung cancer cell lines
```{r}
lung.cls = prism.cl$DepMap_ID[prism.cl$disease=="Lung Cancer"]
LC.prism.achilles = prism.achilles[lung.cls,]
```


#prism.cnv
1)LC.prism.cnv -> prism.cnv data frame only with Lung cancer cell lines
```{r}
lung.cls = prism.cl$DepMap_ID[prism.cl$disease=="Lung Cancer"]
LC.prism.cnv = prism.cnv[lung.cls,]
```
