```{r}
# Topic 2 !
## find most effective drugs!

### have a look at Mesothelioma cell lines
diseases_subtype=prism.cl[, 21]

### in which rows of prism.cl are Mesothelioma cell lines?
p_Meso=c(which(diseases_subtype=="Mesothelioma"))
p_Meso
#-> in those rows of prism.cl are Mesothelioma cell lines:54  57  74 136 142 144 243 273


```


```{r}
# which cell line IDs do belong to those rows
cl1=prism.cl[57,1]
cl2=prism.cl[136,1]
cl3=prism.cl[142,1]
cl4=prism.cl[144,1]
cl5=prism.cl[243,1]
cl6=prism.cl[273,1]
cl7=prism.cl[54,1]
cl8=prism.cl[74,1]

vector_of_cell_lines_meso=c(cl1,cl2, cl3, cl4, cl5, cl6, cl7, cl8, cl8)
vector_of_cell_lines

```
```{r}
# transform prism data set to make searching for cell lines possible
prism_transformed=t(prism)
```


```{r}
vector=c(colnames(prism_trasformed))


which(vector==vector_of_cell_lines[1])
which(vector==vector_of_cell_lines[2])
which(vector==vector_of_cell_lines[3])
which(vector==vector_of_cell_lines[4])
which(vector==vector_of_cell_lines[5])
which(vector==vector_of_cell_lines[6])
which(vector==vector_of_cell_lines[7])
which(vector==vector_of_cell_lines[8])

#-> row of prism data set which belong to mesothelioma cell lines:

row_meso=c(33, 123, 129, 131, 234, 266, 29, 52)

```

###################################################
```{r}
# data set for Mesothelioma cell lines with prism data:

prism_meso=prism[row_meso,]
dim(prism_meso)
```

####################################################
going on with prism_meso

```{r}
# find rowwise minima
n=8
for(i in 0:n){
  print(which.min(prism_meso[i,]))
  i=i+1}

# what are the min values of each row
min(prism_meso[1,], na.rm=TRUE)
min(prism_meso[2,], na.rm=TRUE)
min(prism_meso[3,], na.rm=TRUE)
min(prism_meso[4,], na.rm=TRUE)
min(prism_meso[5,], na.rm=TRUE)
min(prism_meso[6,], na.rm=TRUE)
min(prism_meso[7,], na.rm=TRUE)
min(prism_meso[8,], na.rm=TRUE)
```
```{r}
# take first drug: BRD-K13387373-004-14-5::10 
                                          2167 

# which column in prism
colnames_prism=c(colnames(prism))
which(colnames_prism=="BRD-K13387373-004-14-5::10")

#filter for doses in prism dataset
c2=c(prism_meso[1,2167:2174])
c2

c(prism_meso[1,2959:2966])
```

```{r}
### in which rows of prism.cl are Small Cell Lung Cancer cell lines
p_SCLC=c(which(diseases_subtype=="Small Cell Lung Cancer (SCLC)"))
p_SCLC
#-> in those rows of prism.cl are SCLC cell lines:125 286 324 350 352 390 404 425


```


```{r}
# which cell line IDs do belong to those rows
cl11=prism.cl[125,1]
cl22=prism.cl[286,1]
cl33=prism.cl[324,1]
cl44=prism.cl[350,1]
cl55=prism.cl[352,1]
cl66=prism.cl[390,1]
cl77=prism.cl[404,1]
cl88=prism.cl[425,1]

vector_of_cell_lines_SCLC=c(cl11,cl22, cl33, cl44, cl55, cl66, cl77, cl88)
vector_of_cell_lines_SCLC
```
```{r}
which(vector==vector_of_cell_lines_SCLC[1])
which(vector==vector_of_cell_lines_SCLC[2])
which(vector==vector_of_cell_lines_SCLC[3])
which(vector==vector_of_cell_lines_SCLC[4])
which(vector==vector_of_cell_lines_SCLC[5])
which(vector==vector_of_cell_lines_SCLC[6])
which(vector==vector_of_cell_lines_SCLC[7])
which(vector==vector_of_cell_lines_SCLC[8])

#-> row of prism data set which belong to mesothelioma cell lines:

cell_lines_SCLC=c(111, 279, 319, 346,348, 388, 402, 423)
```


```{r}
# new data fram with SCLC cell lines with prism data

prism_SCLC=prism[cell_lines_SCLC,]
dim(prism_SCLC)
```







```{r}
### have a look at NSCLC cell lines
prism_NSCLC
```


```{r}
diseases=prism.cl[, 20]

p_lung=c(which(diseases=="Lung Cancer"))

p_lung

# number of lication of 
which(p_lung==54)
which(p_lung==57)
which(p_lung==74)
which(p_lung==136)
which(p_lung==142)
which(p_lung==144)
which(p_lung==243)
which(p_lung==273)
which(p_lung==125)
which(p_lung==286)
which(p_lung==324)
which(p_lung==350)
which(p_lung==352)
which(p_lung==390)
which(p_lung==404)
which(p_lung==425)
```


```{r}
prism_NSCLC=prism_lung[-125,]

dim(prism_NSCLC)
```


```{r}
prism_lung=prism[p_lung,]
prism_lung
numbers_lung=c(which(diseases_subtype=="Small Cell Lung Cancer (SCLC)"))
prism_NSCLC=prism_lung[-p_SCLC,]

dim(prism_NSCLC)
```
#############################################
```{r}
# search for most effective drugs in SCLC cell lines
prism_SCLC
```
```{r}
# look at mins rowwise
min(prism_SCLC[1,], na.rm=TRUE)
which.min(prism_SCLC[1,])

## test
prism_SCLC[1,3039]
###-> function which.min does work
```


```{r}
min(prism_SCLC[1,], na.rm=TRUE)
min(prism_SCLC[2,], na.rm=TRUE)
min(prism_SCLC[3,], na.rm=TRUE)
min(prism_SCLC[4,], na.rm=TRUE)
min(prism_SCLC[5,], na.rm=TRUE)
min(prism_SCLC[6,], na.rm=TRUE)
min(prism_SCLC[7,], na.rm=TRUE)
min(prism_SCLC[8,], na.rm=TRUE)
```
```{r}

which.min(prism_SCLC[1,])
which.min(prism_SCLC[2,])
which.min(prism_SCLC[3,])
which.min(prism_SCLC[4,])
which.min(prism_SCLC[5,])
which.min(prism_SCLC[6,])
which.min(prism_SCLC[7,])
which.min(prism_SCLC[8,])
```
```{r}

#BRD-K39484304-001-16-5::10::HTS002 
                              5447 
#BRD-K68202742-001-16-5::10.5396::HTS002 
                                   8159 
#BRD-K51911221-001-01-2::2.5::HTS002 
                               6616 
#BRD-K15409150-001-05-8::10::HTS002 
                              3167 
#BRD-K53734668-003-02-0::10.6299::HTS002 
                                   6791 
#BRD-K60348325-065-09-9::10::HTS002 
                              7359 
#BRD-K35329391-334-01-7::10::HTS002 
                              4991 
#BRD-K47869605-001-32-0::10::HTS002 
                              6159 
```
#used doses: dose1, dose2, dose3, dose4, dose5, dose6, 10, 2.5

##################################################
!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
ab hier alle Zahlen falsch:( mus  ich noch berichtigen
```{r}
# first drug:BRD-K13810148-311-03-2::10::HTS002 

c2=c(prism_SCLC[1,3033:3040])
c2


 
c1=c(1,2,3,4,5,6,7,8,-0.06933266,-0.8475333,-0.4299717,0.2946714,0.606078,-1.107966,-9.615792,-3.193757)
```


```{r}
# create data of first medicament an all of its 8 doses

drug1=matrix(c1, nrow=8,ncol=2, byrow=FALSE)
plot(drug1)



```
```{r}
# get information about first drug:
which(prism.treat$broad_id=="BRD-K13810148-311-03-2")
prism.treat[3273,5]
```

# no doses dependency for medicament 1 (givinostat)
###################################################

```{r}
# second drug: BRD-A66419424-001-02-4::2.5::HTS002 
                               1104 
c2=c(prism_SCLC[2,1097:1104])
c2


 
c1=c(1,2,3,4,5,6,7,8,0.7309511,0.590873,1.218204,0.3833024,0.8667794,-0.4719236,-8.701737,-9.320642)
```


```{r}
# create data of second medicament an all of its 8 doses

drug2=matrix(c1, nrow=8,ncol=2, byrow=FALSE)
plot(drug2, xlab="doses", ylab="effect of drug1 on SCLC cell lines growth")



```
# maybe dose dependency
```{r}
# test for correlation
x=c(1,2,3,4,5,6,7,8)
y=c(0.7309511,0.590873,1.218204,0.3833024,0.8667794,-0.4719236,-8.701737,-9.320642)
cor(x,y)
```

```{r}
# get information about second drug:
which(prism.treat$broad_id=="BRD-A66419424-001-02-4" )
prism.treat[1249,5]
#-> medicament: ixazomib-citrate
```

##################################################

```{r}
# third drug: BRD-K12867552-001-04-7::10::HTS002 
                              2831 
c2=c(prism_SCLC[3,2825:2832])
c2



 
c1=c(1,2,3,4,5,6,7,8,0.7686234,0.5730888,0.6686534,0.820555,1.031086,0.7536717,-8.31886,-2.357724)
```


```{r}
# create data of second medicament an all of its 8 doses

drug3=matrix(c1, nrow=8,ncol=2, byrow=FALSE)
plot(drug3, xlab="doses", ylab="effect of drug3 on SCLC cell lines growth")



```
# not dose dependency
```{r}
# test for correlation
x=c(1,2,3,4,5,6,7,8)
y=c(0.7686234,0.5730888,0.6686534,0.820555,1.031086,0.7536717,-8.31886,-2.357724)
cor(x,y)
```

```{r}
# get information about third drug:
which(prism.treat$broad_id=="BRD-K12867552-001-04-7" )
prism.treat[3074,5]
#-> medicament: PCI-24781
```

```{r}
#fourth drug:BRD-K96104201-001-01-5::10::HTS002 
                             10767 

c2=c(prism_SCLC[6,10761:10768])

# this medicament was the most effective for the 8th cell line of prism_SCLC, too
c2.2=c(prism_SCLC[8, 10761:10768])


c1=c(1,2,3,4,5,6,8,0.2609308,0.6316695,0.1250064,0.6839668,0.4557789,-0.1928866,-10.26673,-6.645097)

c1.2=c(1,2,3,4,5,6,7,8,0.4332369,0.5019201,0.4385701,0.5883302,0.1971815,-0.3786651,-10.14163,-5.28422)
```


```{r}
# create data of second medicament an all of its 8 doses

drug4=matrix(c1, nrow=8,ncol=2, byrow=FALSE)
plot(drug4, xlab="doses", ylab="effect of drug4 on SCLC cell lines growth")

drug4.2=matrix(c1.2, nrow=8,ncol=2, byrow=FALSE)
plot(drug4, xlab="doses", ylab="effect of drug4.2 on SCLC cell lines growth")



```
# not dose dependency, maybe mistake ? Why only effect with such an high dose and NA with higher dose?
```{r}
# test for correlation
x=c(1,2,3,4,5,6,7,8)
y=c(0.2609308,0.6316695,0.1250064,0.6839668,0.4557789,-0.1928866,-10.26673,-6.645097)
cor(x,y)

y.2=c(0.4332369,0.5019201,0.4385701,0.5883302,0.1971815,-0.3786651,-10.14163,-5.28422)
cor(x,y.2)
```

```{r}
# get information about fourth drug:
which(prism.treat$broad_id=="BRD-K96104201-001-01-5" )
prism.treat[10778,5]
#-> medicament: azalomycin-b
```
###################################################

```{r}
# fifth drug: BRD-K15409150-001-05-8::10::HTS002 
                              3167 
c2=c(prism_SCLC[4,3161:3168])


c2.2=c(prism_SCLC[5,3161:3168])
c2.2
 
c1=c(1,2,3,4,5,6,7,8,0.3252984,0.2691451,0.8199687
,0.2753309,-0.3301197,-1.751943,-9.612311,-4.776765)

c1.2=c(1,2,3,4,5,6,7,8,0.6296565,0.1011332,0.3341141,0.05411984,-0.4416629,-1.35251,-9.86566,-3.581259)
```


```{r}
# create data of fifth medicament an all of its 8 doses for cell line 4 and 5 of prism_SCLC 

drug5=matrix(c1, nrow=8,ncol=2, byrow=FALSE)
plot(drug5, xlab="doses", ylab="effect of drug5 on SCLC cell lines growth")

drug5.2=matrix(c1.2, nrow=8,ncol=2, byrow=FALSE)
plot(drug5.2, xlab="doses", ylab="effect of drug5.2 on SCLC cell lines growth")


```
# not dose dependency
```{r}
# test for correlation
x=c(1,2,3,4,5,6,7,8)
y=c(0.3252984,0.2691451,0.8199687
,0.2753309,-0.3301197,-1.751943,-9.612311,-4.776765)

cor(x,y)

y.2=c(0.6296565,0.1011332,0.3341141,0.05411984,-0.4416629,-1.35251,-9.86566,-3.581259)

cor(x,y.2)
```

```{r}
# get information about third drug:
which(prism.treat$broad_id=="BRD-K15409150-001-05-8" )
prism.treat[3401,5]
#-> medicament: penfluridol
```
``####################################################`
```{r}
# get more information about drugs for SCLC:
```


```{r}
# givinostat
which(prism.treat$broad_id=="BRD-K13810148-311-03-2")
#-> row 3273:3280

# proof name
prism.treat[3280,5]

# mode of action
prism.treat[3280,6]
#-> HDAC inhibitor

# target
prism.treat[3280,7]
#-> HDAC1, HDAC2, HDAC3, HDAC4, HDAC5, HDAC6, HDAC7, HDAC8, HDAC9...

# disease.area
prism.treat[3280,8]
#-> NA

# indication
prism.treat[3280,9]
#-> NA
```


```{r}
# ixazomib-citrate
which(prism.treat$broad_id=="BRD-A66419424-001-02-4")
#-> row 1249:1256

# proof name
prism.treat[1249,5]

# mode of action
prism.treat[1249,6]
#-> protease inhibitor

# target
prism.treat[1249,7]
#-> ?...

# disease.area
prism.treat[1249,8]
#-> hematologic malignancy

# indication
prism.treat[1249,9]
#-> multiple myeloma
```
```{r}
# PCI-24781
which(prism.treat$broad_id=="BRD-K12867552-001-04-7")
#-> row 3073:3080

# proof name
prism.treat[3073,5]

# mode of action
prism.treat[3073,6]
#-> HDAC inhibitor

# target
prism.treat[3073,7]
#-> HDAC1, HDAC2, HDAC3, HDAC6

# disease.area
prism.treat[3073,8]
#-> NA

# indication
prism.treat[3073,9]
#-> NA
```
```{r}
# azalomycin-b
which(prism.treat$broad_id=="BRD-K96104201-001-01-5")
#-> row 10777:10784

# proof name
prism.treat[10777,5]

# mode of action
prism.treat[10777,6]
#-> bacterial 50S ribosomal subunit inhibitor

# target
prism.treat[10777,7]
#-> NA

# disease.area
prism.treat[10777,8]
#-> NA

# indication
prism.treat[10777,9]
#-> NA
```


```{r}
# penfluridol
which(prism.treat$broad_id=="BRD-K15409150-001-05-8")
#-> row 3401:3408

# proof name
prism.treat[3401,5]

# mode of action
prism.treat[3401,6]
#-> T-type calcium channel blocker

# target
prism.treat[3401,7]
#-> CACNA1G

# disease.area
prism.treat[3401,8]
#-> neurology/psychiatry

# indication
prism.treat[3401,9]
#-> schizophrenia
```
sum up information about drugs for SCLC:

-> givinostat
-> ixazomib-citrate
-> PCI-24781
-> azalomycin-b
-> penfluridol
```{r}

```

###################################################
```{r}
# now do the same for Mesothelioma cell lines
diseases_subtype=prism.cl[, 21]

p_Meso=c(which(diseases_subtype=="Mesothelioma"))
p_Meso

prism_Meso=prism[p_Meso,]
dim(prism_Meso)
```
```{r}
# 
diseases=prism.cl[, 20]

p_lung=c(which(diseases=="Lung Cancer"))

p_lung

which(p_lung==54)
which(p_lung==57)
which(p_lung==74)
which(p_lung==136)
which(p_lung==142)
which(p_lung==144)
which(p_lung==243)
which(p_lung==273)
which(p_lung==125)
which(p_lung==286)
which(p_lung==324)
which(p_lung==350)
which(p_lung==352)
which(p_lung==390)
which(p_lung==404)
which(p_lung==425)
```

```


